{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-26 draft.tex
Results Section Added

%%%%%%%%% TITLE
\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}

\author{Burak Uzkent\\
Rochester Institute of Technology\\
{\tt\small bxu2522@@rit.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
YoungWoo Seo\\
Independent Robotics Research\\
{\tt\small youngwoo.blank.seo@gmail.com}
}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition on
execution of individual KCFs. To minimize the effect of drifting, we
developed a re-detection module that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
69.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 3\% on AUC on average. Our implementation
ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
faster than DCF (292 fps) for OTB100.
\end{abstract}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran our algorithm using
three publicly available dataset:
VOT2015 \footnote{\url{http://www.votchallenge.net/}},
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.

>>>>

 %%%%%%%%% TITLE
\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}

\author{Burak Uzkent\\
Rochester Institute of Technology\\
{\tt\small bxu2522@@rit.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
YoungWoo Seo\\
Affiliation\\
{\tt\small youngwoo.blank.seo@gmail.com}
}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran our algorithm using
two publicly available datasets:
%VOT2015 \footnote{\url{http://www.votchallenge.net/}},
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects. The proposed $EnKCF$ method can better handle slow motions. Also, the UAVs use mobiles platforms with limited computational power. We believe that the proposed tracker can better fit for tracking from such platforms as it is highly efficient and scale adaptive. Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.

We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success} metrics. Precision is computed as the eucl%
